---
title: "First Pass EDA"
author: "Adam Canton"
date: "7/15/2020"
output: html_document
---
# To DO:
  - Missing Data?
    - Nope! NICE
  - Summary Stats and Distributions for all variables
  - Correlations with response and each other (multicollinearity)
  - Anything look like it needs a transform or a scaling?
  - Create any categoricals or other custom features

Input variables:
# bank client data:
1 - age (numeric)

2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management',
    'retired','self-employed','services','student','technician','unemployed','unknown')
    
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)

4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')

5 - default: has credit in default? (categorical: 'no','yes','unknown')

6 - housing: has housing loan? (categorical: 'no','yes','unknown')

7 - loan: has personal loan? (categorical: 'no','yes','unknown')

# related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone')

9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')

10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')

11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no').
     Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included
     for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
     
# other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)

13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously
     contacted)
     
14 - previous: number of contacts performed before this campaign and for this client (numeric)

15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

# social and economic context attributes
16 - emp.var.rate: employment variation rate - quarterly indicator (numeric)

17 - cons.price.idx: consumer price index - monthly indicator (numeric)

18 - cons.conf.idx: consumer confidence index - monthly indicator (numeric)

19 - euribor3m: euribor 3 month rate - daily indicator (numeric)

20 - nr.employed: number of employees - quarterly indicator (numeric)

Output variable (desired target):
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(tidyverse)
library(olsrr)
library(ggplot2)
library(ggcorrplot)
library(GGally)
library(naniar)
library(reshape2)
library(ggthemes)
library(cowplot)
library(aod)
```

```{r}
# Grab the file Bank Additional Full
BankAF <- read.csv(file = "F:/R For Real/Stats-2-Project-2/bank-additional-full.csv", sep = ";", header = TRUE)

# Change the name of the response from y to Subscription
names(BankAF)[21] <- "Subscription"

# Creating an ID column to spot check train test set data
ID <- seq(1,41188,1)
BankAF <- cbind(BankAF, ID)

#Maybe a new categorical for pdays: New contact v Old contact - this might be captured in previous

# Going to try to create 2 data sets, one for Subscription-yes one for Subscription-no, Sample each one proportionally then recombine into train and test sets
BankAF.yes <- subset(BankAF, Subscription == "yes")
BankAF.no <- subset(BankAF, Subscription == "no")


```

```{r}
# Create Train and Test sets ----
## currently 90/10 Train/Test proportion of yes to no is 11.3% yes to 88.7% no this is slightly off the actual of 9.26% yes to 90.74% no
set.seed(35)
index.yes<-sample(1:dim(BankAF.yes)[1],floor(0.9*dim(BankAF.yes)),replace=F)
train.yes<-BankAF.yes[index.yes,]
test.yes<-BankAF.yes[-index.yes,]

index.no<-sample(1:dim(BankAF.no)[1],floor(0.9*dim(BankAF.no)),replace=F)
train.no<-BankAF.no[index.no,]
test.no<-BankAF.no[-index.no,]

BankAF.train <- rbind(train.yes, train.no)
BankAF.test <- rbind(test.yes, test.no)

# Getting rid of duration  - it will predict nearly perfectly with this in mean prediction error = 0
# Also have to get rid of ID since it was being selected as good explanatory variable
BankAF.train = BankAF.train %>% dplyr::select(-c(duration, ID))
BankAF.test = BankAF.test %>% dplyr::select(-c(duration, ID))

# remove intermediate data sets
rm(test.no, test.yes, train.no, train.yes, BankAF.no, BankAF.yes)
```

```{r}
str(BankAF)
```

```{r}
# No Apparent NA Values, need to check for other NA identifiers
gg_miss_var(BankAF)

na_count <- sapply(BankAF, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


```{r, warning=FALSE}
# Age ----
# The Nos have a massive cut-off around 60 years old. Makes sense these at older ages you would be less interested in getting a TD, than having one already   # payout.
# The median age for yes is actually younger than no

g1 = BankAF %>% ggplot(aes(x = age)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
  facet_wrap(facets = BankAF$Subscription) + xlab("Age") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = age, fill = Subscription)) + geom_histogram(binwidth = 1) + facet_wrap(~BankAF$Subscription) +
  labs(fill = "Subscription") + xlab("Age") + theme(legend.position = "none")

g3 = BankAF %>% group_by(Subscription) %>% summarise(MeanAge = mean(age), Count = n()) %>% ggplot(aes(x = Subscription, y = MeanAge, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = round(MeanAge,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,50), expand = c(0,0)) +
  theme(legend.position = "none", axis.title.x = element_blank())

g4 = BankAF %>% group_by(Subscription) %>% summarise(MedAge = median(age)) %>% ggplot(aes(x = Subscription, y = MedAge, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = round(MedAge,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,50), expand = c(0,0)) +
  theme(legend.position = "none", axis.title.x = element_blank())

g6 = BankAF %>% ggplot(aes(sample = age)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Age")

g5 = ggdraw() + draw_label(sprintf("Summary and Distribution\n of Age:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",min(BankAF$age),summary(BankAF$age)[2], median(BankAF$age), round(mean(BankAF$age),2), summary(BankAF$age)[5], max(BankAF$age)))



plot_grid(g1,g6,g4,g2,g5,g3, ncol = 3, nrow = 2)
```

```{r}
# Duration ---- 
# This will get discarded in final, only here for benchmarking
# From Source Material - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if     # duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input  # should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.

summary(BankAF$duration)
sd(BankAF$duration)

BankAF %>% ggplot(aes(x = duration)) + geom_boxplot() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) + 
  facet_wrap(facets = BankAF$Subscription) + xlab("Duration")

BankAF %>% ggplot(aes(x = duration, fill = Subscription)) + geom_histogram(binwidth = 50) + facet_grid(rows = BankAF$Subscription) +
  labs(fill = "Subscription") + xlab("Duration")

BankAF %>% group_by(Subscription) %>% summarise(MeanDuration = mean(duration), Count = n()) %>% 
  ggplot(aes(x = Subscription, y = MeanDuration, fill = Subscription)) + geom_col(width = 0.5) + 
  geom_text(aes(label = round(MeanDuration,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,600), expand = c(0,0)) +
  theme(legend.position = "none", axis.title.x = element_blank())

BankAF %>% group_by(Subscription) %>% summarise(MedDuration = median(duration)) %>% ggplot(aes(x = Subscription, y = MedDuration, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = round(MedDuration,2)), vjust = -0.5, size = 3) 

```

```{r}
# Campaign ----
# campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
# Heavily right skewed
# Largest number of contacts by far is one
# ~ 98% of campaigns make between 1-10 phone calls, thus ~ 2% of campaigns require more than 10 calls

summary(BankAF$campaign)
sd(BankAF$campaign)

g1 = BankAF %>% ggplot(aes(x = campaign, fill = Subscription)) + geom_boxplot() + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),axis.title.x = element_blank(),
        legend.position = "none") + 
  facet_grid(rows = BankAF$Subscription)

g2 = BankAF %>% ggplot(aes(x = campaign, fill = Subscription)) + geom_histogram(binwidth = 1) + facet_grid(rows = BankAF$Subscription) + xlab("Campaign") +
  theme(legend.position = "none", axis.title.y = element_blank()) + scale_y_continuous(position = "right") + scale_x_continuous(limits = c(0,60))

g3 = BankAF %>% group_by(campaign) %>% summarize(Count = n()) %>% ggplot(aes(x = campaign, y = Count)) + geom_col() + ggtitle("Frequency of Campaign") + 
  geom_text(aes(label = Count), vjust = -0.5, size = 1.5) +scale_y_continuous(limits = c(0,20000), expand = c(0,0)) + 
  scale_x_continuous(limits = c(0, 60), expand = c(0,0)) + xlab("Campaign")

# Not super useful atm
#g4 = BankAF %>% ggplot(aes(sample = campaign)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Campaign")

g5 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\nof Campaign:\nMin -  %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
                     summary(BankAF$campaign)[1], summary(BankAF$campaign)[2],
                     summary(BankAF$campaign)[3],round(summary(BankAF$campaign)[4],2),
                     summary(BankAF$campaign)[5],summary(BankAF$campaign)[6]))

plot_grid(g1,NULL,NULL,g3,g2,NULL,NULL,g5, ncol = 4, nrow = 2, align = "h", rel_widths = c(2,0,0,3))
```

```{r, warning=FALSE}
# Pdays ----
# Not a lot of info here as far as distirbution. Nearly all (39,673) are new contacts, 1,515 are previous contacts.
# Showing the frequency of days since last contact from previous campaigns to previously contacted clients
# Changed the 999 code to 30 in the last graphic to make it easier to visualize

summary(BankAF$pdays)

BankAF %>% group_by(pdays) %>% summarize(Count = n()) %>% ggplot(aes(x = pdays, y = Count)) + geom_col() +
  ggtitle("Frequency of Pdays - Old Customers") + geom_text(aes(label = Count), vjust = -0.5, size = 2) + 
  scale_y_continuous(limits = c(0,1000), expand = c(0,0)) + scale_x_continuous(limits = c(0, 35), expand = c(0,0)) + 
  theme(legend.position = "none")

BankAF %>% mutate(pdays = ifelse(BankAF$pdays >= 30,30,pdays)) %>% group_by(pdays) %>% summarise(Count = n()) %>%
  ggplot(aes(x = pdays, y = Count)) + geom_col() + geom_text(aes(label = Count), vjust = -0.5, size = 3) + 
  ggtitle("Pdays All Clients") + xlab('Pdays (30 indicates new contact)') 

BankAF %>% filter(BankAF$pdays == 999) %>% group_by(Subscription) %>% summarise(Count = n()) %>%
  ggplot(aes(x = Subscription, y = Count, fill = Subscription)) + geom_col(width = 0.5) + 
  ggtitle("New Contacts by Subscription Decision") + geom_text(aes(label = Count), vjust = -0.5, size = 3) + 
  theme(legend.position = "none")
```

```{r}
# Previous ----
# previous: number of contacts performed before this campaign and for this client (numeric)
# 

summary(BankAF$previous)

BankAF %>% ggplot(aes(x = previous, fill = Subscription)) + geom_boxplot() + facet_grid(rows = BankAF$Subscription)

BankAF %>% group_by(previous, Subscription) %>% summarise(Count = n(), .groups = "drop") %>% ggplot(aes(x = previous, y = Count, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = Count), vjust = -0.5, size = 3) + facet_wrap(~Subscription) + theme(legend.position = "none")

```

```{r}
library(MASS)
mylogit.1 <- glm(Subscription ~ ., data = BankAF.train, family = binomial)

```



```{r}
summary(mylogit.1)
```

# This is a bit disheartening essentially we can reach a maximum accuracy of the data set - eg if I classify everything as no I'm right nearly 91% of the time 
```{r}
library(caret)
# Make predictions
probabilities <- mylogit.1 %>% predict(BankAF.test, type = "response")
predicted.classes <- ifelse(probabilities > 0.3, "yes", "no")
# Model accuracy
mean(predicted.classes==BankAF.test$Subscription)

predTable <- tibble(Predicted = as.factor(predicted.classes), Observed = BankAF.test$Subscription)

confusionMatrix(predTable$Predicted, reference = predTable$Observed)
```

```{r}
step.model <- mylogit.1 %>% stepAIC(trace = FALSE)
coef(step.model)
```

```{r}
# Make predictions
probabilities <- step.model %>% predict(BankAF.test, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "yes", "no")
# Model accuracy
mean(predicted.classes==BankAF.test$Subscription)

predTable <- tibble(Predicted = as.factor(predicted.classes), Observed = BankAF.test$Subscription)

confusionMatrix(predTable$Predicted, reference = predTable$Observed)
```































