---
title: "First Pass EDA"
author: "Adam Canton"
date: "7/15/2020"
output: html_document
---
# To DO:
  - Missing Data?
    - Nope! NICE
  - Summary Stats and Distributions for all variables
  - Correlations with response and each other (multicollinearity)
  - Anything look like it needs a transform or a scaling?
  - Create any categoricals or other custom features

Input variables:
# bank client data:
1 - age (numeric)

2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management',
    'retired','self-employed','services','student','technician','unemployed','unknown')
    
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)

4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')

5 - default: has credit in default? (categorical: 'no','yes','unknown')

6 - housing: has housing loan? (categorical: 'no','yes','unknown')

7 - loan: has personal loan? (categorical: 'no','yes','unknown')

# related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone')

9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')

10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')

11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no').
     Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included
     for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
     
# other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)

13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously
     contacted)
     
     
14 - previous: number of contacts performed before this campaign and for this client (numeric)

15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

# social and economic context attributes
16 - emp.var.rate: employment variation rate - quarterly indicator (numeric)

17 - cons.price.idx: consumer price index - monthly indicator (numeric)

18 - cons.conf.idx: consumer confidence index - monthly indicator (numeric)

19 - euribor3m: euribor 3 month rate - daily indicator (numeric)

20 - nr.employed: number of employees - quarterly indicator (numeric)

Output variable (desired target):
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(tidyverse)
library(olsrr)
library(ggplot2)
library(ggcorrplot)
library(GGally)
library(naniar)
library(reshape2)
library(ggthemes)
library(cowplot)
library(aod)
library(ROCR)
```

```{r}
# Grab the file Bank Additional Full - Fill in your file
BankAF <- read.csv(file = "F:/R For Real/Stats-2-Project-2/bank-additional-full.csv", sep = ";", header = TRUE)

# Change the name of the response from y to Subscription
names(BankAF)[21] <- "Subscription"

# Creating an ID column to spot check train test set data
ID <- seq(1,41188,1)
BankAF <- cbind(BankAF, ID)

# SubNum 1:yes 0:no
BankAF <- BankAF %>% mutate(SubNum = ifelse(Subscription == "yes",1,0))

# Creates a numeric data set for PCA
BankAF.Numeric <- BankAF %>% dplyr::select(age, campaign, duration, pdays, previous, emp.var.rate, cons.price.idx, cons.conf.idx, euribor3m, nr.employed, SubNum)


# Going to try to create 2 data sets, one for Subscription-yes one for Subscription-no, Sample each one proportionally then recombine into train and test sets
BankAF.yes <- subset(BankAF, Subscription == "yes")
BankAF.no <- subset(BankAF, Subscription == "no")


```

```{r}
corr <- round(cor(BankAF.Numeric), 3)

ggcorrplot(corr, hc.order = TRUE, type = "lower",
           lab = TRUE, lab_size = 3, method = "circle",
           colors = c("darkorchid4", "white", "springgreen3"),
           title = "Correlations of Continous Variables",
           ggtheme = theme_bw())

```

```{r}
str(BankAF)
summary(BankAF$previous)
```

```{r}
# Boxplots 

# Nothing
g1 = BankAF %>% ggplot(aes(x = log(age), fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Age") + coord_flip() + theme(legend.position = "none")

# Nothing
g2 = BankAF %>% ggplot(aes(x = log(campaign), fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("campaign") + coord_flip() + theme(legend.position = "none")

# Nothing
g3 = BankAF %>% ggplot(aes(x = log(pdays + 1), fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("pdays") + coord_flip() + theme(legend.position = "none")

# Nothing
g4 = BankAF %>% ggplot(aes(x = log(previous +1), fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("previous") + coord_flip() + theme(legend.position = "none")

# Large difference here
g5 = BankAF %>% ggplot(aes(x = emp.var.rate, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("emp.var.rate") + coord_flip() + theme(legend.position = "none")

# Large Difference Here
g6 = BankAF %>% ggplot(aes(x = cons.price.idx, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("cons price") + coord_flip() + theme(legend.position = "none")

# Some difference
g7 = BankAF %>% ggplot(aes(x = cons.conf.idx, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("cons conf") + coord_flip() + theme(legend.position = "none")

# Massive difference in median
g8 = BankAF %>% ggplot(aes(x = euribor3m, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
      facet_wrap(facets = BankAF$Subscription) + xlab("euribor") + coord_flip() + theme(legend.position = "none")

# Large difference
g9 = BankAF %>% ggplot(aes(x = nr.employed, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
      facet_wrap(facets = BankAF$Subscription) + xlab("nr.employed") + coord_flip() + theme(legend.position = "none")

g10 = ggdraw() + draw_label("Continuous Variables by Subscription Decision", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

g11 = BankAF %>% ggplot(aes(x = duration/60, fill = Subscription)) + geom_boxplot() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
      facet_wrap(facets = BankAF$Subscription) + xlab("Duration (mins)") + coord_flip() + theme(legend.position = "none")

g12 = ggdraw() + draw_label('                  Duration in Minutes --->', size = 8)
 
plot_grid(g10, NULL, NULL, g1,g2,g3,g4, g5, g6, g7, g8, g9,NULL,g11, NULL ,nrow = 5, ncol = 3, rel_heights = c(0.5,2,2,2,2), align = "h")
```

```{r, warning = FALSE}
# Categoricals
#Student and Retired most likely to subscribe -  not very high in either around 25% of each
g1 = BankAF %>% group_by(job, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = job, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# No marital status is super different single and unknown roughly 5-10% more likely than married/divorced
g2 = BankAF %>% group_by(marital, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = marital, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Illiterate nearly twice as likely to subscribe as others
g3 = BankAF %>% group_by(education, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = education, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Previous defaults have a 0% subscribe rate
g4 = BankAF %>% group_by(default, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = default, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# No difference across housing
g5 = BankAF %>% group_by(housing, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = housing, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# No difference across loan
g6 = BankAF %>% group_by(loan, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = loan, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Celluar contact has a much higher subscribe rate (14% vs 5%) nearly 3x!
g7 = BankAF %>% group_by(contact, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = contact, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Dec, March, Oct, Sept - Best months
g8 = BankAF %>% group_by(month, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = month, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
     theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Nothing
g9 = BankAF %>% group_by(day_of_week, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = day_of_week, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

# Previous success is a decent predictor of future success
g10 = BankAF %>% group_by(poutcome, Subscription) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = poutcome, y = Perc, fill = Subscription)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g11 = ggdraw() + draw_label("Categorical Variables by Subscription Decision I", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))
g12 = ggdraw() + draw_label("Categorical Variables by Subscription Decision II",  fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))
g13 = ggdraw() + draw_label("Categorical Variables by Subscription Decision III",  fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11, NULL, NULL,g1,g2,g3, nrow = 2, ncol = 3, rel_heights = c(0.5,2))
plot_grid(g12, NULL, NULL,g4,g5,g6, nrow = 2, ncol = 3, rel_heights = c(0.5,2))
plot_grid(g13, NULL, NULL,NULL,g7,g8,g9,g10, nrow = 2, ncol = 4, rel_heights = c(0.5,2))
```

```{r}
BankAF %>% group_by(poutcome, contact) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
  ggplot(aes(x = poutcome, y = Perc, fill = contact)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1)) + scale_fill_manual(values = c("firebrick2", "dodgerblue3")) 

BankAF %>% group_by(month, day_of_week) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
  ggplot(aes(x = month, y = Perc, fill = day_of_week, order = day_of_week)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1)) + 
  scale_fill_manual(breaks = c("mon", "tue", "wed", "thu", "fri"),values = c("firebrick2", "dodgerblue3", "darkorchid4", "gold1", "green1"))

BankAF %>% group_by(housing, education) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
  ggplot(aes(x = housing, y = Perc, fill = education)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1)) 

# making at least double the calls in may as all other months - March a december have the least calls but the highest success rates (nearly 50%)
BankAF %>% group_by(contact, month) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
  ggplot(aes(x = reorder(month,-count), y = count, fill = contact)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1)) + geom_text(aes(label = count), vjust = -0.75, size = 3) + 
  scale_fill_manual(values = c("firebrick2", "dodgerblue3")) 
```


```{r}
# No Apparent NA Values, need to check for other NA identifiers
gg_miss_var(BankAF)

na_count <- sapply(BankAF, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


```{r, warning=FALSE}
# Age ----
# The Nos have a massive cut-off around 60 years old. Makes sense these at older ages you would be less interested in getting a TD, than having one already   # payout.
# The median age for yes is actually younger than no
# Maybe an Age Factor variable would be better?

g1 = BankAF %>% ggplot(aes(x = age, fill = Subscription)) + geom_boxplot() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
  facet_wrap(facets = BankAF$Subscription) + xlab("Age") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = age, fill = Subscription)) + geom_histogram(binwidth = 1) + facet_wrap(~BankAF$Subscription) +
  labs(fill = "Subscription") + xlab("Age") + theme(legend.position = "none")

g3 = BankAF %>% group_by(Subscription) %>% summarise(MeanAge = mean(age), Count = n()) %>% ggplot(aes(x = Subscription, y = MeanAge, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = round(MeanAge,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,50), expand = c(0,0)) +
  theme(legend.position = "none", axis.title.x = element_blank())

g4 = BankAF %>% group_by(Subscription) %>% summarise(MedAge = median(age)) %>% ggplot(aes(x = Subscription, y = MedAge, fill = Subscription)) +
  geom_col(width = 0.5) + geom_text(aes(label = round(MedAge,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,50), expand = c(0,0)) +
  theme(legend.position = "none", axis.title.x = element_blank())

g6 = BankAF %>% ggplot(aes(sample = age)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Age")

g5 = ggdraw() + draw_label(sprintf("Summary and Distribution\n of Age:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",min(BankAF$age),summary(BankAF$age)[2], median(BankAF$age), round(mean(BankAF$age),2), summary(BankAF$age)[5], max(BankAF$age)))



plot_grid(g1,g6,g4,g2,g5,g3, ncol = 3, nrow = 2)
```

```{r}
# Duration ---- 
# This will get discarded in final, only here for benchmarking
# From Source Material - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if     # duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input  # should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.

summary(BankAF$duration)
sd(BankAF$duration)

g1 = BankAF %>% ggplot(aes(x = duration, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Duration") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = duration, fill = Subscription)) + geom_histogram(binwidth = 50) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Duration") + 
      theme(legend.position = "none")

g3 = BankAF %>% group_by(Subscription) %>% summarise(MeanDuration = mean(duration), Count = n()) %>% 
      ggplot(aes(x = Subscription, y = MeanDuration, fill = Subscription)) + geom_col(width = 0.5) + 
      geom_text(aes(label = round(MeanDuration,2)), vjust = -0.5, size = 3) + scale_y_continuous(limits = c(0,600), expand = c(0,0)) +
      theme(legend.position = "none", axis.title.x = element_blank())

g4 = BankAF %>% group_by(Subscription) %>% 
      summarise(MedDuration = median(duration)) %>% 
      ggplot(aes(x = Subscription, y = MedDuration, fill = Subscription)) +
      geom_col(width = 0.5) + geom_text(aes(label = round(MedDuration,2)), vjust = 0, size = 3) + 
      theme(legend.position = "none")

g6 = BankAF %>% ggplot(aes(sample = duration)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Duration")

g5 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Duration:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
  min(BankAF$duration),summary(BankAF$duration)[2], median(BankAF$duration), round(mean(BankAF$duration),2), summary(BankAF$duration)[5], max(BankAF$duration)))

plot_grid(g1,g6,g4,g2,g5,g3, ncol = 3, nrow = 2)
```

```{r}
# Campaign ----
# campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
# Heavily right skewed
# Largest number of contacts by far is one
# ~ 98% of campaigns make between 1-10 phone calls, thus ~ 2% of campaigns require more than 10 calls

summary(BankAF$campaign)
sd(BankAF$campaign)

g1 = BankAF %>% ggplot(aes(x = campaign, fill = Subscription)) + geom_boxplot() + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),axis.title.x = element_blank(),
        legend.position = "none") + 
  facet_grid(rows = BankAF$Subscription)

g2 = BankAF %>% ggplot(aes(x = campaign, fill = Subscription)) + geom_histogram(binwidth = 1) + facet_grid(rows = BankAF$Subscription) + xlab("Campaign") +
  theme(legend.position = "none", axis.title.y = element_blank()) + scale_y_continuous(position = "right") + scale_x_continuous(limits = c(0,60))

g3 = BankAF %>% group_by(campaign) %>% summarize(Count = n()) %>% ggplot(aes(x = campaign, y = Count)) + geom_col() + ggtitle("Frequency of Campaign") + 
  geom_text(aes(label = Count), vjust = -0.5, size = 1.5) +scale_y_continuous(limits = c(0,20000), expand = c(0,0)) + 
  scale_x_continuous(limits = c(0, 60), expand = c(0,0)) + xlab("Campaign")

# Not super useful atm
#g4 = BankAF %>% ggplot(aes(sample = campaign)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Campaign")

g5 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\nof Campaign:\nMin -  %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
                     summary(BankAF$campaign)[1], summary(BankAF$campaign)[2],
                     summary(BankAF$campaign)[3],round(summary(BankAF$campaign)[4],2),
                     summary(BankAF$campaign)[5],summary(BankAF$campaign)[6]))


plot_grid(g1,NULL,NULL,g3,g2,NULL,NULL,g5, ncol = 4, nrow = 2, align = "h", rel_widths = c(2,0,0,3))
```

```{r, warning=FALSE}
# Pdays ----
# Not a lot of info here as far as distirbution. Nearly all (39,673) are new contacts, 1,515 are previous contacts.
# Showing the frequency of days since last contact from previous campaigns to previously contacted clients
# Changed the 999 code to 30 in the last graphic to make it easier to visualize

summary(BankAF$pdays)

g1 = BankAF %>% group_by(pdays) %>% summarize(Count = n()) %>% ggplot(aes(x = pdays, y = Count)) + geom_col() +
      ggtitle("Frequency of Pdays - Old Customers") + geom_text(aes(label = Count), vjust = -0.5, size = 2) + 
      scale_y_continuous(limits = c(0,1000), expand = c(0,0)) + scale_x_continuous(limits = c(0, 35), expand = c(0,0)) + 
      theme(legend.position = "none", axis.title.y = element_blank())

g2 = BankAF %>% mutate(pdays = ifelse(BankAF$pdays >= 30,30,pdays)) %>% group_by(pdays) %>% summarise(Count = n()) %>%
      ggplot(aes(x = pdays, y = Count)) + geom_col() + geom_text(aes(label = Count), vjust = 0, size = 2) + 
      ggtitle("Pdays All Clients") + xlab('Pdays (30 indicates new contact)')  + 
      theme(axis.title.y = element_blank())

g3 = BankAF %>% filter(BankAF$pdays == 999) %>% group_by(Subscription) %>% summarise(Count = n()) %>%
      ggplot(aes(x = Subscription, y = Count, fill = Subscription)) + geom_col(width = 0.5) + 
      ggtitle("New Contacts by Subscription Decision") + geom_text(aes(label = Count), vjust = 0, size = 3) + 
      theme(legend.position = "none", axis.title.y = element_blank())

g4 = ggdraw() + 
      draw_label(sprintf("Summary and Distribution\n of Pdays:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
      min(BankAF$pdays),summary(BankAF$pdays)[2], median(BankAF$pdays), round(mean(BankAF$pdays),2), summary(BankAF$pdays)[5], max(BankAF$pdays)))

plot_grid(NULL,NULL,g1,g2,NULL,NULL,g3,g4, nrow = 4, ncol = 2, rel_heights = c(0.25,2,0.25,2))
```

```{r}
# Previous ----
# previous: number of contacts performed before this campaign and for this client (numeric)
# 

g1 = BankAF %>% ggplot(aes(x = previous, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Previous") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = previous, fill = Subscription)) + geom_histogram(binwidth = 1) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Previous") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = duration)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Previous")

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Previous:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
  min(BankAF$previous),summary(BankAF$previous)[2], median(BankAF$previous), round(mean(BankAF$previous),2), summary(BankAF$previous)[5], max(BankAF$previous)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```

```{r}
# Emp.Var.Rate ----


g1 = BankAF %>% ggplot(aes(x = emp.var.rate, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Employment Variation Rate") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = emp.var.rate, fill = Subscription)) + geom_histogram(binwidth = 1) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Employment Variation Rate") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = emp.var.rate)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Employment Variation Rate") + 
      theme(axis.title.y = element_blank())

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Emp.var.rate:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
  min(BankAF$emp.var.rate),summary(BankAF$emp.var.rate)[2], median(BankAF$emp.var.rate), round(mean(BankAF$emp.var.rate),2), summary(BankAF$emp.var.rate)[5],
  max(BankAF$emp.var.rate)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```

```{r}
# Cons.price.idx ----


g1 = BankAF %>% ggplot(aes(x = cons.price.idx, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Consumer Price Index") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = cons.price.idx, fill = Subscription)) + geom_histogram(binwidth = 1) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Consumer Price Index") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = cons.price.idx)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Consumer Price Index") + 
      theme(axis.title.y = element_blank())

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Consumer Price Index:\nMin - %s\n1st Qu. - %s\nMedian - %s\nMean - %s\n3rd Qu. - %s\nMax - %s",
  min(BankAF$cons.price.idx),summary(BankAF$cons.price.idx)[2], median(BankAF$cons.price.idx), round(mean(BankAF$cons.price.idx),2),
  summary(BankAF$cons.price.idx)[5],max(BankAF$cons.price.idx)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```

```{r}
# Cons.conf.idx ----


g1 = BankAF %>% ggplot(aes(x = cons.conf.idx, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Consumer Confidence Index") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = cons.conf.idx, fill = Subscription)) + geom_histogram(binwidth = 1) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Consumer confidence Index") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = cons.conf.idx)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Consumer Confidence Index") + 
      theme(axis.title.y = element_blank())

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Consumer Confidence Index:\nMin : %s\n1st Qu.: %s\nMedian: %s\nMean: %s\n3rd Qu.: %s\nMax: %s",
  min(BankAF$cons.conf.idx),summary(BankAF$cons.conf.idx)[2], median(BankAF$cons.conf.idx), round(mean(BankAF$cons.conf.idx),2),
  summary(BankAF$cons.conf.idx)[5],max(BankAF$cons.conf.idx)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```

```{r}
# Euribor3m ----


g1 = BankAF %>% ggplot(aes(x = euribor3m, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Euribor3m") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = euribor3m, fill = Subscription)) + geom_histogram(binwidth = 1) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Euribor3m") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = euribor3m)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Euribor3m") + 
      theme(axis.title.y = element_blank())

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Euribor3m:\nMin : %s\n1st Qu.: %s\nMedian: %s\nMean: %s\n3rd Qu.: %s\nMax: %s",
  min(BankAF$euribor3m),summary(BankAF$euribor3m)[2], median(BankAF$euribor3m), round(mean(BankAF$euribor3m),2),
  summary(BankAF$euribor3m)[5],max(BankAF$euribor3m)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```

```{r}
# nr.employed ----


g1 = BankAF %>% ggplot(aes(x = nr.employed, fill = Subscription)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none") + 
      facet_wrap(facets = BankAF$Subscription) + xlab("Number Employed") + coord_flip()

g2 = BankAF %>% ggplot(aes(x = nr.employed, fill = Subscription)) + geom_histogram(binwidth = 50) +
      facet_grid(rows = BankAF$Subscription) +
      labs(fill = "Subscription") + xlab("Number Employed") + 
      theme(legend.position = "none", axis.title.y = element_blank())

g3 = BankAF %>% ggplot(aes(sample = nr.employed)) + stat_qq_line() + stat_qq() + xlab("Quantile") + ylab("Number Employed") + 
      theme(axis.title.y = element_blank())

g4 = ggdraw() + 
  draw_label(sprintf("Summary and Distribution\n of Number Employed:\nMin : %s\n1st Qu.: %s\nMedian: %s\nMean: %s\n3rd Qu.: %s\nMax: %s",
  min(BankAF$nr.employed),summary(BankAF$nr.employed)[2], median(BankAF$nr.employed), round(mean(BankAF$nr.employed),2),
  summary(BankAF$nr.employed)[5],max(BankAF$nr.employed)))

plot_grid(g1,g2,g3,g4, ncol = 2, nrow = 2)

```














